LogChunks: A Data Set for Build Log Analysis

### 2020-03-05 msr-paper/paper.tex
include loads of text and graphics from thesis, fix graphics, start adapting heading levels
proposing some adjustments from reviewer feedback

For \logchunks, we queried GHTorrent on 2018-04-01 for the three
most popular repositories of each of the 30 most popular languages.
Among the resulting repositories are, for example, \texttt{git/git},
\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.

\paragraph{Build Sampling}
To sample the builds for \logchunks we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

@@

\paragraph{Results}
In total, from 2020-10-15 to 2020-10-17, we sent out emails to 246 developers. Of these, 32 could
not be delivered. We performed the sending out in three batches and used the first author's academic email address as the sender. All emails were specific to each recipient. We only sent one mail per recipient. We received answers from 61 developers, corresponding to
144 build logs with a response rate of 24.8\%. Compared to typical response rates to cold calling known from Software Engineering~\cite{smith2013improving}, this is very high. We believe that our personalization and the ease of use for the participant are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer. Indeed, we only received seven replies from developers along the lines of ``done.''

>>>>

For \logchunks, we queried GHTorrent from 2018-04-01 for the three
most popular repositories of each of the 30 most popular languages
to cover a broad range of development languages.
Among the resulting repositories are, for example, \texttt{git/git},
\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.

\paragraph{Build Sampling}
To sample the builds for \logchunks we keep the most recent ten of the status 
\emph{failed}~\cite{travis2009buildstatus}. We check up to 1,000 builds per 
repository to ensure predictable termination of the log collection.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

@@

\paragraph{Results}
In total, from 2019-10-15 to 2019-10-17, we sent out emails to 246 developers. Of these, 32 could
not be delivered. We performed the sending out in three batches and used the first author's academic email address as the sender. All emails were specific to each recipient. We only sent one mail per recipient. We received answers from 61 developers, corresponding to
144 build logs with a response rate of 24.8\%. Compared to typical response rates to cold calling known from Software Engineering~\cite{smith2013improving}, this is very high. We believe that our personalization and the ease of use for the participant are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer. Indeed, we only received seven replies from developers along the lines of ``done.''
